Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-28 ms.tex
fixing color description.

The left panel of Figure \ref{fig:miller} is calculated assuming a
constant low value for the radiative efficiency of $\epsilon_X =
10^{-4}$, typical of those estimated for low luminosity AGN (e.g.,
\citealt{Ho:2009a}).  The right panel luminosities are calculated
instead assuming an efficiency of $\epsilon_X= \epsilon_{\rm
  bol}\epsilon_{\rm rad}$ that depends on the Eddington ratio
as predicted by MHD sheaing box simulations by \citet{Sharma+2007} (see eq.~[\ref{eq:efficiency}] and surrounding discussion).  Shown for comparison are the X-ray measurements (green stars) and upper limits
(gray triangles) from the sample of early-type galaxies compiled by
\citet{Miller+15} (cf.~\citealt{Gallo+10}).  A green line shows the
best power-law fit to the X-ray luminosity from \citet{Miller+15},
given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with
$\alpha = -0.2$ (see also \citealt{Zhang+09, Pellegrini10, Gallo+10}).
Also shown are the maximum accretion rates, respectively, for
thermally stable accretion (eq.~[\ref{eq:Mdotmax}]; yellow), as set by
SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]; teal), and as allowed by
Compton heating feedback (eq.~[\ref{eq:MdotC}]; red).

>>>>

The left panel of Figure \ref{fig:miller} is calculated assuming a
constant low value for the radiative efficiency of $\epsilon_X =
10^{-4}$, typical of those estimated for low luminosity AGN (e.g.,
\citealt{Ho:2009a}).  The right panel luminosities are calculated
instead assuming an efficiency of $\epsilon_X= \epsilon_{\rm
  bol}\epsilon_{\rm rad}$ that depends on the Eddington ratio as
predicted by MHD sheaing box simulations by \citet{Sharma+2007} (see
eq.~[\ref{eq:efficiency}] and surrounding discussion).  Shown for
comparison are the X-ray measurements (black stars) and upper limits
(gray triangles) from the sample of early-type galaxies compiled by
\citet{Miller+15} (cf.~\citealt{Gallo+10}).  A black line shows the
best power-law fit to the X-ray luminosity from \citet{Miller+15},
given by $\langle L_X/L_{\rm edd}\rangle \sim \Mbh^\alpha$ with
$\alpha = -0.2$ (see also \citealt{Zhang+09, Pellegrini10, Gallo+10}).
Also shown are the maximum accretion rates, respectively, for
thermally stable accretion (eq.~[\ref{eq:Mdotmax}]; yellow), as set by
SN Ia blow-out (eq.~[\ref{eq:eddr_Ia}]; teal), and as allowed by
Compton heating feedback (eq.~[\ref{eq:MdotC}]; pink).
